An Open System for\\ Managing Short Programming Exercises

### 2013-08-09 paper/talk.tex
question about adoption
more work on questions slide

\begin{itemize}
\item Are short exercises useful?
  \begin{itemize}
  \item Do you use short exercises in your courses currently?
  \item Would {\em you} want to use short exercises in your course?
  \item What experiments should we do to measure effect on outcomes?
  \end{itemize}
\item How do we most effectively incorporate short exercises into a course?
  \begin{itemize}
  \item How do we know what exercises should be assigned?
  \item In what order should the exercises be assigned?
  \item What mix of short exercises vs.\ larger assignments?
  \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
\item Are short exercises useful?
  \begin{itemize}
  \item Do you use short exercises in your courses currently?
    \begin{itemize}
    \item If so, how?
    \item If not, would you be interested in starting to use them?
    \end{itemize}
  \item What experiments should we do to measure effect on outcomes?
  \end{itemize}
\item How should we most effectively incorporate short exercises into a course?
  \begin{itemize}
  \item How do we know what exercises should be assigned?
  \item In what order should the exercises be assigned?
  \item What mix of short exercises vs.\ larger assignments?
  \item How to motivate students to attempt exercises?
  \end{itemize}
\end{itemize}
